Missing the Point\(\colon\) Non-Convergence in Multiple Imputation Procedures

### 2020-04-03 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Removed excess plots from manuscript. Ready for feedback.

The multiple imputation method can be roughly divided into 3 steps. First, each missing value in an incomplete dataset is 'imputed' (i.e., filled in) several times. Next, the analysis of scientific interest is performed on each of the completed datasets. And finally, the results of these analyses are pooled into a single aggregated statistic. The theoretical foundation of these streps was laid by Rubin [1972, -@rubin87]. For an accessible and comprehensive introduction to MI from an applied perspective, see e.g. @buur18. In this paper, we focus on the first of these steps: the algorithmic procedure with which the missing values are imputed.

@@

```{r, include = FALSE}
load("../Results/25percentmiss.Rdata")
source("../2.CreateFigures.R")
```

```{r}
bias_means_plot + R_means_plot + AC_means_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of means, 25% missingness")
```

```{r}
bias_sds_plot + R_sds_plot + AC_sds_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of variances, 25% missingness")
```

```{r}
bias_ests_plot + bias_R_sq_plot + cov_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of effects, 25% missingness")

```{r, include = FALSE}
load("../Results/50percentmiss.Rdata")
source("../2.CreateFigures.R")
```

```{r}
bias_means_plot + R_means_plot + AC_means_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of means, 50% missingness")
```

```{r}
bias_sds_plot + R_sds_plot + AC_sds_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of variances, 50% missingness")
```

```{r}
bias_ests_plot + bias_R_sq_plot + cov_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of effects, 50% missingness")

@@

```{r}
bias_ests_plot + bias_R_sq_plot + cov_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of effects, 75% missingness")

```{r, include = FALSE}
load("../Results/95percentmiss.Rdata")
source("../2.CreateFigures.R")
```

```{r}
bias_means_plot + R_means_plot + AC_means_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of means, 95% missingness")
```

```{r}
bias_sds_plot + R_sds_plot + AC_sds_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of variances, 95% missingness")
```

```{r}
bias_ests_plot + bias_R_sq_plot + cov_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of effects, 95% missingness")

>>>>

The multiple imputation method can be roughly divided into 3 steps. First, each missing value in an incomplete dataset is 'imputed' (i.e., filled in) several times. Next, the analysis of scientific interest is performed on each of the completed datasets. And finally, the results of these analyses are pooled into a single aggregated statistic. The theoretical foundation of these streps was laid by Rubin [-@rubin76, -@rubin87]. For an accessible and comprehensive introduction to MI from an applied perspective, see e.g. @buur18. In this paper, we focus on the first of these steps: the algorithmic procedure with which the missing values are imputed.

@@

@@

```{r}
bias_ests_plot + bias_R_sq_plot + cov_plot + plot_layout(nrow = 3) + plot_annotation(title = "Convergence of effects, 75% missingness")
```

```{r, echo = FALSE}
load("../Results/combined.Rdata")

dat %>% ggplot(aes(x = T, y = bias.R.s, color = miss)) + 
  geom_point() +
  geom_line() +
  ylab(expression(paste("Bias in ", hat(R ^ 2)))) +
  labs(colour = "Legend: missingness percentage") +
  plot_annotation(title = "The effect of missingness percentage, an example")

### 2020-04-03 3.Thesis/1.SimulationStudy/Writeup/manuscript.tex
Removed excess plots from manuscript. Ready for feedback.

The multiple imputation method can be roughly divided into 3 steps.
First, each missing value in an incomplete dataset is `imputed' (i.e.,
filled in) several times. Next, the analysis of scientific interest is
performed on each of the completed datasets. And finally, the results of
these analyses are pooled into a single aggregated statistic. The
theoretical foundation of these streps was laid by Rubin
\citeyearpar[1972,][]{rubin87}. For an accessible and comprehensive
introduction to MI from an applied perspective, see e.g.~\citet{buur18}.
In this paper, we focus on the first of these steps: the algorithmic
procedure with which the missing values are imputed.

@@

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-7-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-8-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-9-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-11-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-12-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-13-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-15-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-16-1} \end{flushleft}

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-17-1} \end{flushleft}

For 25\% miss, no bias in estimated means, Rh flat from 30 it. (but
\textless1.1 for it\textgreater11), AC never high but stable after 40
it. Bias in estimated variances only if it=1 or maybe 2?, while Rh of
chain variances is flat around it 25 (smaller than 1.1 for
it\textgreater9), and AC never positive, flat around it 30. Bias in
estimated reg. coeff. only pronounced for the first iteration., while
coverage rates are ok immediately on average, variance explained is
marginally underestimated (bias of 0.5\% on an effect of 19.25\%).

>>>>

The multiple imputation method can be roughly divided into 3 steps.
First, each missing value in an incomplete dataset is `imputed' (i.e.,
filled in) several times. Next, the analysis of scientific interest is
performed on each of the completed datasets. And finally, the results of
these analyses are pooled into a single aggregated statistic. The
theoretical foundation of these streps was laid by Rubin
\citeyearpar[\citeyearpar{rubin87}]{rubin76}. For an accessible and
comprehensive introduction to MI from an applied perspective, see
e.g.~\citet{buur18}. In this paper, we focus on the first of these
steps: the algorithmic procedure with which the missing values are
imputed.

@@

\begin{flushleft}\includegraphics{manuscript_files/figure-latex/unnamed-chunk-6-1} \end{flushleft}
